Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-01-11 _tex/paper2.tex
Built site for gh-pages

\section{Introduction}\label{sec-introduction}

@@

\section{Thurstone's theory}\label{sec-thurstone_theory}

@@

\section{The two critical issues in CJ
literature}\label{sec-theory-issues}

@@

\subsection{The Case V and the statistical analysis of CJ
data}\label{sec-theory-issue1}

@@

\subsubsection{The assumption of equal dispersions between
stimuli}\label{sec-theory-issue1a}

@@

\subsubsection{The assumption of zero correlation between
stimuli}\label{sec-theory-issue1b}

@@

\subsection{The disconnect between trait measurement and hypothesis
testing}\label{sec-theory-issue2}

@@

\section{Updating the theoretical and statistical
model}\label{sec-theory}

This section uses the structural approach to causal inference
\citep{Pearl_2009, Pearl_et_al_2016} to articulate a theoretical model
that captures the core principles of Thurstone's theory. The model also
incorporates various assessment design features relevant to CJ
experiments, such as the selection of judges, stimuli, and comparisons.
Finally, the section employs Bayesian statistical methods to transform
these theoretical and practical elements into a statistical model that
facilitates the analysis of pairwise comparison data. See
Section~\ref{sec-appendix} for an overview of the statistical and causal
inference concepts required for the development of this section.

\subsection{The theoretical model}\label{sec-theory-theoretical}

@@

\subsubsection{The population model}\label{sec-theory-theoretical_P}

@@

\subsubsection{The sample-comparison
model}\label{sec-theory-theoretical_SC}

@@

\subsection{From theory to statistics}\label{sec-theory-statistics}

\section{Discussion}\label{sec-discuss}

\subsection{Findings}\label{sec-discuss-finding}

\subsection{Limitations and further
research}\label{sec-discuss-limitations}

\section{Conclusion}\label{sec-conclusion}

@@

\section*{Declarations}\label{declarations}
\addcontentsline{toc}{section}{Declarations}

@@

\section{Appendix}\label{sec-appendix}

@@

\subsection{Empirical research and randomized
experiments}\label{sec-appendix-A}

@@

\subsection{Empirical research under causal
inference}\label{sec-appendix-B}

Unlike classical statistical modeling, which focuses primarily on
summarizing data and inferring associations, the \emph{causal inference}
framework is designed to identify causes and estimate their effects
using data \citep{Shaughnessy_et_al_2010, Neal_2020}. The framework uses
rigorous mathematical techniques to address the \emph{fundamental
problem of causality}
\citep{Pearl_2009, Pearl_et_al_2016, Morgan_et_al_2014}. This problem
revolves around the question, ``What would have happened `in the world'
under different circumstances?'' This question introduces the concept of
counterfactuals, which are instrumental in understanding and defining
causal effects.

\emph{Counterfactuals} are hypothetical scenarios that are
\emph{contrary to fact}, where alternative outcomes resulting from a
given cause are neither observed nor observable
\citep{Neal_2020, Counterfactual_2024}. The structural approach to
causal inference \citep{Pearl_2009, Pearl_et_al_2016} provides a formal
framework for defining counterfactuals. For instance, in the scenario
described in Section~\ref{sec-appendix-A}, the approach begins by
defining the \emph{individual causal effect} (ICE) as the difference
between each student's potential outcomes:
\(\tau_{i} = Y_{i}|do(T_{i}=1) - Y_{i}|do(T_{i}=2)\). Here,
\(do(T_{i}=t)\) represents the intervention operator,
\(Y_{i}|do(T_{i}=1)\) represents the potential outcome under
intervention \(T_{i}=1\), and \(Y_{i}|do(T_{i}=1)\) represents the
potential outcome under intervention \(T_{i}=2\). Note that if a student
is assigned to intervention \(T_{i}=1\), the potential outcome under
\(T_{i}=2\) becomes a counterfactual, as it is no longer observed nor
observable. To address the challenge of unobserved counterfactuals, the
approach extends the ICE to the \emph{average causal effect} (ACE):
\(\tau = E[\tau_{i}] = E[Y_{i}|do(T_{i}=1)]- E[Y_{i}|do(T_{i}=2)]\),
representing the average difference between observed potential outcomes
and their counterfactual counterparts. Notably, the approach extends the
ACEs for categorical and continuous variables \(T\), ensuring broad
applicability across different causal scenarios.

@@

For instance, if researchers are unable to conduct the randomized
experiments described in Section~\ref{sec-appendix-A} and instead rely
on observational data, they can still estimate the ACE provided a
variable \(X\), such as the socio-economic status of the school, blocks
all non-causal paths between the teaching method \(T\) to the outcome
\(Y\) without opening any new ones. Under these conditions, the ACE can
be estimated from associational quantities as
\(\tau = E_{X}\left[ E[Y_{i}| T_{i}=1, X] - E[Y_{i}| T_{i}=2, X] \right]\),
where \(E_{X}[\cdot]\) represents the marginal expected value over \(X\)
\citep{Morgan_et_al_2014}.

\subsection{SCMs and DAGs}\label{sec-appendix-C}

@@

Figures \ref{fig-dags_scms1}, \ref{fig-dags_scms2},
\ref{fig-dags_scms3}, \ref{fig-dags_scms4}, and \ref{fig-dags_scms5}
display these five fundamental building blocks. The left panels of the
figures show the formal mathematical models, represented by the SCMs,
defined in terms of a set of \emph{endogenous} variables
\(V=\{X,Z,Y\}\), a set of \emph{exogenous} variables
\(E=\{e_{X},e_{Z},e_{Y}\}\), and a set of functions
\(F=\{f_{X},f_{Z},f_{Y}\}\)
\citep{Pearl_2009, Cinelli_et_al_2020, Neal_2020}. Endogenous variables
are those whose causal mechanisms a researcher chooses to model
\citep{Neal_2020}. In contrast, exogenous variables represent
\emph{errors} or \emph{disturbances} arising from omitted factors that
the investigator chooses not to model explicitly
\citep[pp.~27,68]{Pearl_2009}. Lastly, the functions, referred to as
\emph{structural equations}, express the endogenous variables as
non-parametric functions of other variables. These functions use the
symbol `\(:=\)' to denote the asymmetrical causal dependence of the
variables and the symbol `\(\perp\!\!\!\perp\)' to represent
\emph{d-separation}, a concept akin to (conditional) independence.

@@

\[
\begin{aligned}
  X & := f_{X}(e_{X}) \\
  Y & := f_{Y}(e_{Y}) \\
  e_{X} & \perp\!\!\!\perp e_{Y}
\end{aligned}
\]

@@

\end{minipage}%
\newline
\begin{minipage}{0.50\linewidth}

@@

\[
\begin{aligned}
  X & := f_{X}(e_{X}) \\
  Y & := f_{Y}(X,e_{Y}) \\
  e_{X} & \perp\!\!\!\perp e_{Y}
\end{aligned}
\]

@@

\[
\begin{aligned}
  X & := f_{X}(e_{X}) \\
  Z & := f_{Z}(X,e_{Z}) \\
  Y & := f_{Y}(Z,e_{Y}) \\
  e_{X} & \perp\!\!\!\perp e_{Y} \\
  e_{X} & \perp\!\!\!\perp e_{Z} \\
  e_{Z} & \perp\!\!\!\perp e_{Y}
\end{aligned}
\]

@@

\[
\begin{aligned}
  X & := f_{X}(Z,e_{X}) \\
  Z & := f_{Z}(e_{Z}) \\
  Y & := f_{Y}(Z,e_{Y}) \\
  e_{X} & \perp\!\!\!\perp e_{Y} \\
  e_{X} & \perp\!\!\!\perp e_{Z} \\
  e_{Z} & \perp\!\!\!\perp e_{Y}
\end{aligned}
\]

@@

\[
\begin{aligned}
  X & := f_{X}(e_{X}) \\
  Z & := f_{Z}(X,Y,e_{Z}) \\
  Y & := f_{Y}(e_{Y}) \\
  e_{X} & \perp\!\!\!\perp e_{Y} \\
  e_{X} & \perp\!\!\!\perp e_{Z} \\
  e_{Z} & \perp\!\!\!\perp e_{Y}
\end{aligned}
\]

@@

A careful examination of the figures highlights the assumptions
underlying these building blocks. Figures \ref{fig-scm_bb1} and
\ref{fig-mdag_bb1} depict two unconnected nodes, representing a scenario
where variables \(X\) and \(Y\) are not causally related. Figures
\ref{fig-scm_bb2} and \ref{fig-mdag_bb2} illustrate two connected nodes,
representing a scenario where a \emph{parent} node \(X\) exerts a causal
influence on a \emph{child} node \(Y\). Consequently, \(Y\) is
considered a \emph{descendant} of \(X\). Figures \ref{fig-scm_bb3} and
\ref{fig-mdag_bb3} depict a \emph{chain}, where \(X\) influences \(Z\),
and \(Z\) influences \(Y\). In this configuration, \(X\) is a parent
node of \(Z\), which is a parent node of \(Y\). This structure creates a
\emph{directed path} between \(X\) and \(Y\). Consequently, \(X\) is an
\emph{ancestor} of \(Y\), and \(Z\) fully \emph{mediates} the
relationship between the two. Figures \ref{fig-scm_bb4} and
\ref{fig-mdag_bb4} illustrate a \emph{fork}, where variables \(X\) and
\(Y\) are both influenced by \(Z\). Here, \(Z\) is a parent node that
\emph{confounds} the relationship between \(X\) and \(Y\). Finally,
Figures \ref{fig-scm_bb5} and \ref{fig-mdag_bb5} show a \emph{collider},
where variables \(X\) and \(Y\) are concurrent causes of \(Z\). In this
configuration, \(X\) and \(Y\) are not causally related to each other
but both influence \(Z\) (an \emph{inmorality}). Notably, in all SCMs,
the errors are assumed to be independent of each other and from all
other variables in the graph, as evidenced by the pairwise relations
\(e_{X} \perp\!\!\!\perp e_{Y}\), \(e_{X} \perp\!\!\!\perp e_{Z}\), and
\(e_{Z} \perp\!\!\!\perp e_{Y}\).

@@

\subsection{The flow of association and causation in
DAGs}\label{sec-appendix-D}

@@

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

>>>>

Introduction

@@

Thurstone's theory

@@

The two critical issues in CJ literature

@@

\section{The Case V and the statistical analysis of CJ
data}\label{sec-theory-issue1}

@@

\subsection{The assumption of equal dispersions between
stimuli}\label{sec-theory-issue1a}

@@

\subsection{The assumption of zero correlation between
stimuli}\label{sec-theory-issue1b}

@@

\section{The disconnect between trait measurement and hypothesis
testing}\label{sec-theory-issue2}

@@

Updating the theoretical and statistical model

This section uses the structural approach to causal inference
\citep{Pearl_2009, Pearl_et_al_2016} to articulate a theoretical model
that captures the core principles of Thurstone's theory. The model also
incorporates various assessment design features relevant to CJ
experiments, such as the selection of judges, stimuli, and comparisons.
Finally, the section employs Bayesian inference methods to transform
these theoretical and practical elements into a statistical model that
facilitates the analysis of pairwise comparison data. See
Section~\ref{sec-appendix} for an overview of the statistical and causal
inference concepts required for the development of this section.

\section{The theoretical model}\label{sec-theory-theoretical}

@@

\subsection{The population model}\label{sec-theory-theoretical_P}

@@

\subsection{The sample-comparison
model}\label{sec-theory-theoretical_SC}

@@

\section{From theory to statistics}\label{sec-theory-statistics}

Bayesian inference procedures offer three key advantages. First, they
are well-suited to handling complex and overparameterized models,
enabling researchers to estimate models where the number of parameters
exceeds the number of observations for estimation
\citep{Baker_1998, Kim_et_al_1999}. Second, they allow researchers to
incorporate prior information, which helps constrain parameters within
specified bounds. This capability addresses challenges such as
non-convergence or improper parameter estimation that often arise in
complex models when analyzed with frequentist methods
\citep{Martin_et_al_1975, Seaman_et_al_2011}. Finally, Bayesian methods
are particularly effective at drawing inferences from small sample
sizes, where relying on the asymptotic properties of frequentist
approaches may not be justified
\citep{Baldwin_et_al_2013, Lambert_et_al_2006, Depaoli_2014}.

Discussion

\section{Findings}\label{sec-discuss-finding}

\section{Limitations and further
research}\label{sec-discuss-limitations}

Conclusion

@@

Declarations

@@

Appendix

@@

\section{Empirical research and randomized
experiments}\label{sec-appendix-A}

@@

\section{Identification under causal inference}\label{sec-appendix-B}

Unlike classical statistical modeling, which focuses primarily on
summarizing data and inferring associations, the \emph{causal inference}
framework is designed to identify causes and estimate their effects
using data \citep{Shaughnessy_et_al_2010, Neal_2020}. The framework uses
rigorous mathematical techniques to address the \emph{fundamental
problem of causality}
\citep{Pearl_2009, Pearl_et_al_2016, Morgan_et_al_2014}. This problem
revolves around the question, ``What would have happened `in the world'
under different circumstances?'' This question introduces the concept of
counterfactuals, which are instrumental in defining and identifying
causal effects.

\emph{Counterfactuals} are hypothetical scenarios that are
\emph{contrary to fact}, where alternative outcomes resulting from a
given cause are neither observed nor observable
\citep{Neal_2020, Counterfactual_2024}. The structural approach to
causal inference \citep{Pearl_2009, Pearl_et_al_2016} provides a formal
framework for defining counterfactuals. For instance, in the scenario
described in Section~\ref{sec-appendix-A}, the approach begins by
defining the \emph{individual causal effect} (ICE) as the difference
between each student's potential outcomes:
\(\tau_{i} = Y_{i}|do(T_{i}=1) - Y_{i}|do(T_{i}=2)\). Here,
\(do(T_{i}=t)\) represents the intervention operator,
\(Y_{i}|do(T_{i}=1)\) represents the potential outcome under
intervention \(T_{i}=1\), and \(Y_{i}|do(T_{i}=1)\) represents the
potential outcome under intervention \(T_{i}=2\). Note that if a student
is assigned to intervention \(T_{i}=1\), the potential outcome under
\(T_{i}=2\) becomes a counterfactual, as it is no longer observed nor
observable. To address the challenge of unobserved counterfactuals, the
approach extends the ICE to the \emph{average causal effect} (ACE):
\(\tau = E[\tau_{i}] = E[Y_{i}|do(T_{i}=1)]- E[Y_{i}|do(T_{i}=2)]\),
representing the average difference between observed potential outcomes
and their counterfactual counterparts.

@@

For instance, if researchers are unable to conduct the randomized
experiments described in Section~\ref{sec-appendix-A} and instead rely
on observational data, they can still estimate the ACE provided a
variable \(X\), such as the socio-economic status of the school, blocks
all non-causal paths between the teaching method \(T\) to the outcome
\(Y\) without opening any new ones. Under these conditions, the ACE can
be estimated from associational quantities as \(\tau =\)
\(E[Y_{i}|do(T_{i}=1)]- E[Y_{i}|do(T_{i}=2)] =\)
\(E_{X}\left[ E[Y_{i}| T_{i}=1, X] - E[Y_{i}| T_{i}=2, X] \right]\),
where \(E_{X}[\cdot]\) represents the marginal expected value over \(X\)
\citep{Morgan_et_al_2014}. Notably, the approach extends the ACE for a
continuous variable \(T\) as \(\tau =\) \(E[Y_{i}|do(T_{i}=t)] =\)
\(d E_{X}\left[ E[Y_{i}| T_{i}=t, X]\right]/ dt\), ensuring broad
applicability across different causal scenarios
\citep[pp.~45]{Neal_2020}.

\section{SCMs and DAGs}\label{sec-appendix-C}

@@

Figures \ref{fig-dags_scms1}, \ref{fig-dags_scms2},
\ref{fig-dags_scms3}, \ref{fig-dags_scms4}, and \ref{fig-dags_scms5}
display these five fundamental building blocks. The left panels of the
figures show the formal mathematical models, represented by the SCMs,
defined in terms of a set of \emph{endogenous} variables
\(V=\{X_{1},X_{2},X_{3}\}\), a set of \emph{exogenous} variables
\(E=\{e_{X1},e_{X2},e_{X3}\}\), and a set of functions
\(F=\{f_{X1},f_{X2},f_{X3}\}\)
\citep{Pearl_2009, Cinelli_et_al_2020, Neal_2020}. Endogenous variables
are those whose causal mechanisms a researcher chooses to model
\citep{Neal_2020}. In contrast, exogenous variables represent
\emph{errors} or \emph{disturbances} arising from omitted factors that
the investigator chooses not to model explicitly
\citep[pp.~27,68]{Pearl_2009}. Lastly, the functions, referred to as
\emph{structural equations}, express the endogenous variables as
non-parametric functions of other variables. These functions use the
symbol `\(:=\)' to denote the asymmetrical causal dependence of the
variables and the symbol `\(\perp\!\!\!\perp\)' to represent
\emph{d-separation}, a concept akin to (conditional) independence.

@@

\[
\begin{aligned}
  X_{1} & := f_{X1}(e_{X1}) \\
  X_{3} & := f_{X3}(e_{X3}) \\
  e_{X1} & \perp\!\!\!\perp e_{X3}
\end{aligned}
\]

@@

@@

\[
\begin{aligned}
  X_{1} & := f_{X1}(e_{X1}) \\
  X_{3} & := f_{X3}(X_{1},e_{X3}) \\
  e_{X1} & \perp\!\!\!\perp e_{X3}
\end{aligned}
\]

@@

\[
\begin{aligned}
  X_{1} & := f_{X1}(e_{X1}) \\
  X_{2} & := f_{X2}(X_{1},e_{X2}) \\
  X_{3} & := f_{X3}(X_{2},e_{X3}) \\
  e_{X1} & \perp\!\!\!\perp e_{X2} \\
  e_{X1} & \perp\!\!\!\perp e_{X3} \\
  e_{X2} & \perp\!\!\!\perp e_{X3}
\end{aligned}
\]

@@

\[
\begin{aligned}
  X_{1} & := f_{X1}(X_{2},e_{X1}) \\
  X_{2} & := f_{X2}(e_{X2}) \\
  X_{3} & := f_{X3}(X_{2},e_{X3}) \\
  e_{X1} & \perp\!\!\!\perp e_{X2} \\
  e_{X1} & \perp\!\!\!\perp e_{X3} \\
  e_{X2} & \perp\!\!\!\perp e_{X3}
\end{aligned}
\]

@@

\[
\begin{aligned}
  X_{1} & := f_{X1}(e_{X1}) \\
  X_{2} & := f_{X2}(X_{1},X_{3},e_{X2}) \\
  X_{3} & := f_{X3}(e_{X3}) \\
  e_{X1} & \perp\!\!\!\perp e_{X2} \\
  e_{X1} & \perp\!\!\!\perp e_{X3} \\
  e_{X2} & \perp\!\!\!\perp e_{X3}
\end{aligned}
\]

@@

A careful examination of the figures highlights the assumptions
underlying these building blocks. Figures \ref{fig-scm_bb1} and
\ref{fig-mdag_bb1} depict two unconnected nodes, representing a scenario
where variables \(X_{1}\) and \(X_{3}\) are not causally related.
Figures \ref{fig-scm_bb2} and \ref{fig-mdag_bb2} illustrate two
connected nodes, representing a scenario where a \emph{parent} node
\(X_{1}\) exerts a causal influence on a \emph{child} node \(X_{3}\). In
this setup, \(X_{3}\) is considered a \emph{descendant} of \(X_{1}\).
Additionally, \(X_{1}\) and \(X_{3}\) are described as \emph{adjacent}
because an edge directly connects them. Figures \ref{fig-scm_bb3} and
\ref{fig-mdag_bb3} depict a \emph{chain}, where \(X_{1}\) influences
\(X_{2}\), and \(X_{2}\) influences \(X_{3}\). In this configuration,
\(X_{1}\) is a parent node of \(X_{2}\), which is a parent node of
\(X_{3}\). This structure creates a \emph{directed path} between
\(X_{1}\) and \(X_{3}\). Consequently, \(X_{1}\) is an \emph{ancestor}
of \(X_{3}\), and \(X_{2}\) fully \emph{mediates} the relationship
between the two. Figures \ref{fig-scm_bb4} and \ref{fig-mdag_bb4}
illustrate a \emph{fork}, where variables \(X_{1}\) and \(X_{3}\) are
both influenced by \(X_{2}\). Here, \(X_{2}\) is a parent node that
\emph{confounds} the relationship between \(X_{1}\) and \(X_{3}\).
Finally, Figures \ref{fig-scm_bb5} and \ref{fig-mdag_bb5} show a
\emph{collider}, where variables \(X_{1}\) and \(X_{3}\) are concurrent
causes of \(X_{2}\). In this configuration, \(X_{1}\) and \(X_{3}\) are
not causally related to each other but both influence \(X_{2}\) (an
\emph{inmorality}). Notably, in all SCMs, the errors are assumed to be
independent of each other and from all other variables in the graph, as
evidenced by the pairwise relations \(e_{X1} \perp\!\!\!\perp e_{X2}\),
\(e_{X1} \perp\!\!\!\perp e_{X3}\), and
\(e_{X2} \perp\!\!\!\perp e_{X3}\).

@@

\section{The probabilistic implications of DAGs}\label{sec-appendix-D}

After completing the identification process outlined in
Section~\ref{sec-appendix-B}, researchers estimate the ACE using
Bayesian inference methods. Bayesian inference calculates the
probability of a set of parameters \(\theta\), enabling researchers to
use their distributions to represent the ACE. The approach begins by
defining two probability distributions: the likelihood of the data,
\(P(X_{1}, X_{2}, \dots, X_{n} | \theta)\), and the prior distribution,
\(P(\theta)\) \citep{Everitt_et_al_2010}. Here, \(X_{n}\) represents a
random variable, and for simplicity, \(\theta\) denotes a parameter
space of dimension one. After observing empirical data, researchers
update these priors to posterior distributions using Bayes' rule
\citep{Jeffreys_1998}:

\begin{equation}\phantomsection\label{eq-bayes_rule}{
P(\theta| X_{1}, X_{2}, \dots, X_{n}) = \frac{P(X_{1}, X_{2}, \dots, X_{n} | \theta) \cdot P(\theta)}{P(X_{1}, X_{2}, \dots, X_{n})}
}\end{equation}

Researchers can further simplify the posterior updating process in
Equation~\ref{eq-bayes_rule} into two steps: integrating new empirical
data, which is defined by the likelihood, with the parameter update,
which is determined by the priors, as demonstrated in equation
Equation~\ref{eq-prop_rule}. This simplification is possible because the
denominator on the right-hand side of Equation~\ref{eq-bayes_rule} acts
as a normalizing constant, independent of \(\theta\).

\begin{equation}\phantomsection\label{eq-prop_rule}{
P(\theta| X_{1}, X_{2}, \dots, X_{n}) \propto P(X_{1}, X_{2}, \dots, X_{n} | \theta) \cdot P(\theta)
}\end{equation}

Temporarily setting aside the definition of prior distributions, it is
important to note that the posterior updating process depends on the
assumptions underlying the likelihood of the data. However, as the
number of random variables, \(n\), increases, this joint distribution
becomes quickly intractable \citep{Neal_2020}. This is evident from
Equation~\ref{eq-like_chain}, where the likelihood distribution is
re-expressed in terms of chained conditional distributions.

\begin{equation}\phantomsection\label{eq-like_chain}{
P(X_{1}, X_{2}, \dots, X_{n}|\theta) = P(X_{1}|\theta) \prod^{n}_{i=2} P(X_{i} | X_{i-1}, \dots, X_{1}, \theta )
}\end{equation}

To address the complexity of the likelihood, researchers simplify the
distribution by assuming that variables exhibit specific local
(in)dependencies. These assumptions improve model tractability and
streamline the estimation process. Researchers formalize these local
(in)dependencies using directed acyclic graphs (DAGs). DAGs represent
the probabilistic implications of these assumptions by relying on three
key principles: the local Markov assumption, the minimality assumption,
and the causal edges assumption. The \emph{local Markov assumption}
defines the statistical independencies implied by a DAG. It states that
a variable is independent of all its non-descendants, given its parents
\citep{Neal_2020}. The \emph{minimality assumption} identifies the
statistical dependencies implied by a DAG. It asserts that every pair of
adjacent variables are dependent \citep{Neal_2020}. Finally, the
\emph{causal edges assumption} establishes causal relationships between
parents and their children in a DAG by stating that every parent is a
direct cause of their children \citep{Neal_2020}. Figure
Figure~\ref{fig-ACflow} illustrates the flow of association and
causation in graphs.

@@

This lead to the \emph{Bayesian Network factorization} of
Equation~\ref{eq-like_chain}.

\begin{equation}\phantomsection\label{eq-net_factor}{
P(X_{1}, X_{2}, \dots, X_{n}|\theta) = P(X_{1}|\theta) \prod^{n}_{i=2} P(X_{i} | pa(X_{i}), \theta )
}\end{equation}

@@

References
